---
title: A quick start to agdist 
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A quick start to agdist}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: sentence
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7
)

# avoid check where vignette filename must equal the vignette title
options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup, include = FALSE}
pkg = 'agdist' #so we can easily switch names
library(pkg, character.only = TRUE)
```

## Overview

**`r pkg`** is designed to allow you convenient computation of antigenic distance metrics for influenza (and possibly other pathogens). 



## Installation

**`r pkg`** is not yet on CRAN. You need to install it from GitHub as follows:

* Install the `remotes` package
* Install **`r pkg`** with `remotes::install_github('ahgroup/agdist')`


## Starting Example

Here is a simple example to illustrate what **`r pkg`** does.

Consider 


## Another example


## Next steps

You just learned the basics of using **`r pkg`** to compute antigenic distances.
To dig deeper, you should continue with [this vignette](./moredetails.html).
